---
title: "CV Anna Malinowska"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme: 
      version: 3
      bootswatch: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(flexdashboard)
library(dplyr)
library(tidyverse)
library(stringr)
library(tm)
library(tidytext)
library(wordcloud)
library(ggwordcloud)
library(ggplot2)
library(plotly)
library(ggsci)
library(ggrepel)
library(bslib)
library(lubridate)
library(DT)
library(htmltools)
```


```{r CV data preparation, include=FALSE}
# First I need to rewrite my CV into a dataframe which will be possible to plot later on
# Each part of CV is created row by row, so it will be easy do add next experience, skills etc. in the future
## Preparing Experience data frame

Experience <- list()

Experience[[length(Experience) + 1]] <- list(
  start_date = as.Date("2023-07-01"),
  end_date   = as.Date(Sys.Date()),
  where_1       = "Wageningen University & Research",
  where_2 = "UNLOCK",
  role    = "Postdoctoral Researcher")

Experience[[length(Experience) + 1]] <- list(
  start_date = as.Date("2022-07-01"),
  end_date   = as.Date(Sys.Date()),
  where_1       = "Wageningen University & Research",
  where_2 = "Laboratory of Microbiology",
  role    = "Postdoctoral Researcher")

Experience[[length(Experience) + 1]] <- list(
  start_date = as.Date("2020-06-01"),
  end_date   = as.Date("2022-06-01"),
  where_1       = "Wageningen University & Research",
  where_2 = "Human Nutrition Division",
  role    = "Postdoctoral Researcher")

Experience[[length(Experience) + 1]] <- list(
  start_date = as.Date("2013-10-01"),
  end_date   = as.Date("2022-09-30"),
  where_1       = "Poznań University of Life Sciences",
  where_2 = "Department of Human Nutrition and Dietetics",
  role    = "Assistant Professor")

Experience[[length(Experience) + 1]] <- list(
  start_date = as.Date("2013-05-01"),
  end_date   = as.Date("2013-07-31"),
  where_1       = "Biofarm LLC",
  where_2 = "Research and Development",
  role    = "Senior medical documentation specialist")

Experience_df <- bind_rows(Experience) %>%
  mutate(role_wrapped = str_wrap(role, width = 18),
         where_1_wrapped = str_wrap(where_1, width = 18),
         where_2_wrapped = str_wrap(where_2, width = 18)) %>%
  arrange(start_date) %>%
  mutate(where_1 = factor(where_1, levels = unique(where_1)))
 

## Preparing Education data frame
Education <- list()

Education[[length(Education) + 1]] <- list(
  start_date = as.Date("2008-10-01"),
  end_date   = as.Date("2013-09-01"),
  where_1       = "Poznań University of Life Sciences",
  where_2 = "Faculty of Food Science and Nutrition",
  role    = "PhD")

Education[[length(Education) + 1]] <- list(
  start_date = as.Date("2003-10-01"),
  end_date   = as.Date("2008-07-01"),
  where_1       = "Poznań University of Life Sciences",
  where_2 = "Faculty of Food Science and Nutrition",
  role    = "MSc")

Education_df <- bind_rows(Education) %>%
  mutate(role_wrapped = str_wrap(role, width = 18),
         where_1_wrapped = str_wrap(where_1, width = 18),
         where_2_wrapped = str_wrap(where_2, width = 18)) %>%
  arrange(start_date) %>%
  mutate(where_1 = factor(where_1, levels = unique(where_1)))

## Preparing Trainings data frame
Trainings <- list()

Trainings[[length(Trainings) + 1]] <- list(
  start_date = as.Date("2022-06-13"),
  end_date   = as.Date("2022-07-04"),
  where_1       = "Wageningen University & Research",
  where_2       = "Graduate School VLAG ",
  title    = "Scientific Artwork\nwith Adobe Illustrator",
  type = "other",
  key_outcomes = "drawing, designing figures and infographics in Adobe Illustrator")

Trainings[[length(Trainings) + 1]] <- list(
  start_date = as.Date("2020-10-27"),
  end_date   = as.Date("2020-10-29"),
  where_1       = "Wageningen University & Research",
  where_2       = "Graduate School VLAG ",
  title    = "Applied Statistics",
  type = "analytical",
  key_outcomes = "basic analyses in R, sample size, comparing meand and medians")

Trainings[[length(Trainings) + 1]] <- list(
  start_date = as.Date("2020-10-13"),
  end_date   = as.Date("2020-10-15"),
  where_1       = "Wageningen University & Research",
  where_2       = "Graduate School VLAG ",
  title    = "Chemometrics",
  type = "analytical",
  key_outcomes = "multivariate analysis in R, modelling, regression, clustering")

Trainings[[length(Trainings) + 1]] <- list(
  start_date = as.Date("2019-03-01"),
  end_date   = as.Date("2020-09-01"),
  where_1       = "Poznań University of Life Sciences",
  where_2       = "Support and development Center",
  title    = "Academic teaching training",
  type = "pedagogical",
  key_outcomes = "creating and composing infographics and slides, sketchnoting, problem-solving teaching, blended learning, using social media in the teaching process")

Trainings[[length(Trainings) + 1]] <- list(
  start_date = as.Date("2019-11-14"),
  end_date   = as.Date("2019-12-15"),
  where_1       = "Poznań University of Life Sciences",
  where_2       = "Collegium Wratislaviense",
  title    = "Academic tutors school",
  type = "pedagogical",
  key_outcomes = "mentoring, tutoring")

Trainings[[length(Trainings) + 1]] <- list(
  start_date = as.Date("2012-04-01"),
  end_date   = as.Date("2012-06-30"),
  where_1       = "Danone Research",
  where_2       = "Centre for Specialised Nutrition",
  title    = "Erasmus scholarship",
  type = "nutritional",
  key_outcomes = "Performing laboratory analysis, analysis of scientific literature concerning the impact of fetal and early childhood nutrition on the susceptibility to obesity and metabolic diseases in adulthood")

Trainings[[length(Trainings) + 1]] <- list(
  start_date = as.Date("2008-07-01"),
  end_date   = as.Date("2008-09-15"),
  where_1       = "Nestle",
  where_2       = "Call Centre",
  title    = "Internship",
  type = "nutritional",
  key_outcomes = "Phone consulting in the field of child and infant nutrition")

Trainings_df <- bind_rows(Trainings)

Trainings_df<- Trainings_df %>%
  mutate(where_1 = paste0("<b>", where_1, "</b>")) %>%
   mutate(where_1_wrapped = str_wrap(where_1, width = 18),
          title_wrapped = str_wrap(title, width = 25)) %>%
  arrange(start_date) %>%
  mutate(where_1 = factor(where_1, levels = unique(where_1)))

## Preparing Projects data frame

Projects <- list()

Projects[[length(Projects) + 1]] <- list(
  start_date = as.Date("2022-07-01"),
  end_date   = Sys.Date(),
  where_1 = "Wageningen University & Research",
  where_2 = "Laboratory of Microbiology",
  title       = "The intestinal microbiota composition and development of preterm infants in early life",
  short_title = "Gut microbiota of preterm infants",
  role    = "Investigator (data analysis)")

Projects[[length(Projects) + 1]] <- list(
  start_date = as.Date("2025-01-01"),
  end_date   = Sys.Date(),
  where_1 = "Wageningen University & Research",
  where_2 = "Laboratory of Microbiology",
  title       = "The effect of galacto-oligosaccharides (GOS) or chicory fructo-oligosaccharides (FOS) versus a placebo on bowel habits in children with functional constipation. (INSIDE study)",
  short_title = "GOS, FOS and contipation in children",
  role    = "Investigator (data analysis)")

Projects[[length(Projects) + 1]] <- list(
  start_date = as.Date("2023-01-01"),
  end_date   = Sys.Date(),
  where_1 = "Wageningen University & Research",
  where_2 = "Laboratory of Microbiology",
  title       = "The effect of a 6 weeks intervention with synbiotics on the recovery speed of the gut microbiota after antibiotic treatment in Dutch toddlers (TOBBI study)",
  short_title = "Microbial recovery after antibiotic treatment",
  role    = "Co-supervisor (PhD candidate)")

Projects[[length(Projects) + 1]] <- list(
  start_date = as.Date("2022-07-01"),
  end_date   = Sys.Date(),
  where_1 = "Wageningen University & Research",
  where_2 = "Laboratory of Microbiology",
  title       = "FucoQuest: The impact of fucosylated human milk oligosaccharides on infant gut microbiome, metabolism and gut function",
  short_title = "2FL enrichment and microbial profile in children",
  role    = "Investigator (data analysis)")

Projects[[length(Projects) + 1]] <- list(
  start_date = as.Date("2023-01-01"),
  end_date   =as.Date("2024-01-01"),
  where_1 = "Wageningen University & Research",
  where_2 = "Laboratory of Microbiology",
  title       = "The effect of a multispecies probiotic on reducing the incidence of antibiotic-associated diarrhoea in children",
  short_title = "Probiotics and diarrhoea in children",
  role    = "Investigator (data analysis)")

Projects[[length(Projects) + 1]] <- list(
  start_date = as.Date("2021-02-01"),
  end_date   = as.Date("2022-06-30"),
  where_1 = "Wageningen University & Research",
  where_2 = "Human Nutrition Division",
  title       = "Elucidating the Role of Human Small Intestine Microbiota in Explaining Differences in Postprandial Glucose Responses (GLYSIMI)",
  short_title = "Glucose response and small intestinal microbiota",
  role    = "Investigator (data analysis)")

Projects[[length(Projects) + 1]] <- list(
  start_date = as.Date("2016-03-01"),
  end_date   = as.Date("2020-03-01"),
  where_1 = "Poznań University of Life Sciences",
  where_2 = "Department of Human Nutrition and Dietetics",
  title       = "Gut microbiota as the link between dietary patterns and human metabolism",
  short_title = "Dietary patterns and gut microbiota",
  role    = "Principal Investigator")

Projects[[length(Projects) + 1]] <- list(
  start_date = as.Date("2017-03-01"),
  end_date   = as.Date("2022-09-01"),
  where_1 = "Poznań University of Life Sciences",
  where_2 = "Department of Human Nutrition and Dietetics",
  title       = "Influence of maternal choline intake and non-alcoholic fatty liver disease during pregnancy and lactation on endocrine pancreas development in the offspring",
  short_title = "Metabolic programming by maternal choline intake and NAFLD",
  role    = "Investigator (biochemical analyses)")

Projects[[length(Projects) + 1]] <- list(
  start_date = as.Date("2015-08-01"),
  end_date   = as.Date("2019-02-01"),
  where_1 = "Poznań University of Life Sciences",
  where_2 = "Department of Human Nutrition and Dietetics",
  title       = "Relationships between fat discrimination, frequency of eating high-fat foods, and gene polymorphism - determination of body weight and lipid metabolism",
  short_title = "Fat taste project",
  role    = "Investigator (biochemical and nutritional analyses)")

Projects[[length(Projects) + 1]] <- list(
  start_date = as.Date("2015-08-01"),
  end_date   = as.Date("2019-02-01"),
  where_1 = "Poznań University of Life Sciences",
  where_2 = "Department of Human Nutrition and Dietetics",
  title       = "Assessment of choline intake and choline metabolism in pregnant women",
  short_title = "Choline in pregnant women",
  role    = "Investigator (nutritional analyses)")

Projects[[length(Projects) + 1]] <- list(
  start_date = as.Date("2014-01-01"),
  end_date   = as.Date("2014-12-31"),
  where_1 = "Poznań University of Life Sciences",
  where_2 = "Department of Human Nutrition and Dietetics",
  title       = "Relationship between choline gut metabolism and cardiovascular diseases",
  short_title = "Choline and CVDs",
  role    = "Principal Investigator")

Projects[[length(Projects) + 1]] <- list(
  start_date = as.Date("2013-01-01"),
  end_date   = as.Date("2013-12-31"),
  where_1 = "Poznań University of Life Sciences",
  where_2 = "Department of Human Nutrition and Dietetics",
  title       = "Genetic determinants of homocysteine metabolism",
  short_title = "Homocysteine metabolism",
  role    = "Principal Investigator")

Projects_df <- bind_rows(Projects) %>% 
  mutate(role_wrapped = str_wrap(role, width = 18)) %>%
  mutate(where_1_wrapped = str_wrap(where_1, width = 18)) %>%
  arrange(start_date) %>%
  mutate(where_1 = factor(where_1, levels = unique(where_1))) %>%
  mutate(title_wrapped = str_wrap(title, width = 18))

## Preparing Skills data frame
biostatistical_skills <- list()

biostatistical_skills[[length(biostatistical_skills) + 1]] <- list(
  start_date = as.Date("2019-09-16"),
  end_date   = Sys.Date(),
  where_1 = "Poznań University of Life Sciences",
  where_2 = "Department of Human Nutrition and Dietetics",
  software       = "Statistica",
  skill    = "regression analysis")

biostatistical_skills[[length(biostatistical_skills) + 1]] <- list(
  start_date = as.Date("2019-12-12"),
  end_date   = Sys.Date(),
  software       = "Statistica",
  where_1 = "Poznań University of Life Sciences",
  where_2 = "Department of Human Nutrition and Dietetics",
  skill    = "multivariate analyses")

biostatistical_skills[[length(biostatistical_skills) + 1]] <- list(
  start_date = as.Date("2020-01-16"),
  end_date   = Sys.Date(),
  software       = "Statistica",
  where_1 = "Poznań University of Life Sciences",
  where_2 = "Department of Human Nutrition and Dietetics",
  skill    = "basic statistical analyses (comparing means, medians)")

biostatistical_skills[[length(biostatistical_skills) + 1]] <- list(
  start_date = as.Date("2020-10-01"),
  end_date   = Sys.Date(),
  software       = "R",
  where_1 = "Wageningen University & Research",
  where_2 = "Human Nutrition Division",
  skill    = "data wrangling, reshaping, visualizations with ggplot2")

biostatistical_skills[[length(biostatistical_skills) + 1]] <- list(
  start_date = as.Date("2021-06-01"),
  end_date   = Sys.Date(),
  where_1 = "Wageningen University & Research",
  where_2 = "Human Nutrition Division",
  software       = "R",
  skill    = "microbiome analysis with phyloseq, microViz, vegan etc")


biostatistical_skills[[length(biostatistical_skills) + 1]] <- list(
  start_date = as.Date("2021-06-01"),
  end_date   = Sys.Date(),
  where_1 = "Wageningen University & Research",
  where_2 = "Human Nutrition Division",
  software       = "Linux",
  skill    = "PICRUSt 2.0")

biostatistical_skills[[length(biostatistical_skills) + 1]] <- list(
  start_date = as.Date("2022-07-01"),
  end_date   = Sys.Date(),
  where_1 = "Wageningen University & Research",
  where_2 = "Laboratory of Microbiology",
  software       = "Linux",
  skill    = "16S sequencing data analysis with NG-Tax 2.0")

biostatistical_skills[[length(biostatistical_skills) + 1]] <- list(
  start_date = as.Date("2023-06-01"),
  end_date   = Sys.Date(),
  where_1 = "Wageningen University & Research",
  where_2 = "Laboratory of Microbiology",
  software       = "R",
  skill    = "proteomic analysis")

biostatistical_skills[[length(biostatistical_skills) + 1]] <- list(
  start_date = as.Date("2024-01-01"),
  end_date   = Sys.Date(),
  where_1 = "Wageningen University & Research",
  where_2 = "Laboratory of Microbiology",
  software       = "Linux",
  skill    = "bash scripting, Metaphlan, HUMAnN, cutadapt, Megahit")


biostatistical_skills_df <- bind_rows(biostatistical_skills)

biostatistical_skills_df <- biostatistical_skills_df %>% 
  mutate(skill_wrapped = str_wrap(skill, width = 18)) %>%
  mutate(where_1_wrapped = str_wrap(where_1, width = 30)) %>%
  arrange(start_date) %>%
  mutate(where_1_wrapped = factor(where_1_wrapped, levels = rev(unique(where_1_wrapped)))) %>%
  mutate(label_x = start_date + months(6))

```


```{css}
.skill-badge {
  display: inline-block;
  padding: 10px 16px;
  margin: 4px;
  border-radius: 15px;
  color: white;
  font-size: 16px;
  font-weight: 500;
}

.green  { background-color: #28a745; }
.blue   { background-color: #007bff; }
.orange { background-color: #fd7e14; }
.purple { background-color: #6f42c1; }
}

```

Timelines & wordclouds
================================

Summary {data-height=200}
---------------------------------------------------------------------------------------

### Years of experience {data-width=250}

```{r experience_years}
years_of_experience<- round(as.numeric(time_length(interval((Education_df %>% filter(role == "PhD") %>% pull(start_date)),Sys.Date()), "years")), 1)

valueBox(years_of_experience, caption = "Years of Experience",
         icon = "fa-business-time", color = "info")
```

### Years analysing data {data-width=250}

```{r percentage_data_analysis}
years_of_experience_data<- round(as.numeric(time_length(interval((Experience_df %>% filter(where_2 == "Human Nutrition Division") %>% pull(start_date)),Sys.Date()), "years")), 1)

percentage_years_data_analist<- round(years_of_experience_data * 100 / years_of_experience,0)

gauge(value = percentage_years_data_analist,
    min = 0,
    max = 100,
    label = "% analysing data")
```

### Analyzed Clinical & Omics Datasets {data-width=250}

```{r datasets_analyzed}
valueBox("30+", caption = "Analyzed Clinical & Omics Datasets",
         icon = "fa-database", color = "primary")
```

### Analyzed samples {data-width=250}

```{r samples_analyzed}
valueBox("5000+", caption = "Analyzed samples",
         icon = "fa-chart-bar", color = "primary")
```

Core expertise & skills {data-height=100 .tabset}
--------------------------------------------------

### Core expertise

```{r core expertise}
div(
  style = "padding:10px;",

  span("Human Nutrition", class = "skill-badge green"),
  span("Clinical Research", class = "skill-badge green"),
  span("Dietary Assessment", class = "skill-badge green"),

  span("Gut Microbiome", class = "skill-badge orange"),

  span("Multi-Omics", class = "skill-badge purple"),

  span("Biostatistics", class = "skill-badge blue")
)
```

### Study designs

```{r Study designs, echo=FALSE}
div(
  style = "padding:10px;",
  
  span("Observational studies (cross-sectional, cohort, case-control)", class = "skill-badge green"),
  span("Human intervention studies", class = "skill-badge green"),
  span("RCTs", class = "skill-badge green"),
  span("pragmatic clinical studies", class = "skill-badge green"))

```

### Dataset expertise

```{r Dataset expertise, echo=FALSE}
div(
  style = "padding:10px;",
  
  span("Clinical and nutritional", class = "skill-badge green"),
  span("Dietary intake and anthropometric data", class = "skill-badge green"),
  span("Gut microbiome data (16S rRNA sequencing, shotgun metagenomics, functional profiling)", class = "skill-badge orange"),
  span("proteomics and metaproteomics datasets", class = "skill-badge purple"),
  span("continuous glucose monitoring (CGM)", class = "skill-badge green"),
  span("longitudinal and compositional", class = "skill-badge purple")
)

```

### Statistical methods

```{r Statistical methods, echo=FALSE}
div(
  style = "padding:10px;",
  
  span("Linear and logistic regression", class = "skill-badge blue"),
  span("mixed-effects modelling", class = "skill-badge blue"),
  span("multivariate analysis", class = "skill-badge blue"),
  span("longitudinal data analysis", class = "skill-badge blue"),
  span("confounding adjustment", class = "skill-badge blue"),
  span("multiple testing correction", class = "skill-badge blue"),
  span("power/sample size considerations", class = "skill-badge blue")
)

```


Education & Experience {data-height=600}
--------------------------------------------------

### Education & Experience timeline {data-width=600}

```{r main timeline, echo=FALSE}
main_timeline<- ggplot(Experience_df, aes(y = where_2_wrapped)) +
  geom_segment(aes(x = start_date, xend = end_date, yend = where_2_wrapped), color = "gray45", alpha = 0.4, linewidth = 7) +
  geom_point(aes(x = start_date, fill = role_wrapped), shape = 21, size = 8) +
  geom_point(aes(x = end_date, fill = role_wrapped), shape = 21, size = 6) +
  geom_segment(data = Education_df, aes(x = start_date, xend = end_date, yend = where_2_wrapped), color = "gray25", alpha = 0.4, linewidth = 7) +
  geom_point(data = Education_df, aes(x = start_date, fill = role_wrapped), shape = 21, size = 8) +
  geom_point(data = Education_df, aes(x = end_date, fill = role_wrapped), shape = 21,size = 6) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  facet_grid(rows = vars(where_1_wrapped), scales = "free")+
  scale_fill_nejm(name = "Position")+
  guides(fill = guide_legend(override.aes = list(size = 4)))+
  theme_minimal() +
  theme(
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_text(angle = 60, hjust = 1, size = 10),
    legend.position = "bottom") +
  coord_cartesian(clip = "off")

ggplotly(main_timeline)%>%
  layout(
    legend = list(
      orientation = "h",
      x = 0.5,
      y = -0.3,
      yref = "paper",
      xanchor = "center",
      yanchor = "top"
    ),
    margin = list(l = 70, r = 70, b = 150)
  )

```

### Wordcloud {data-width=400}

```{r main wordcloud, echo=FALSE}

word_counts_Ed_Exp <- bind_rows(Education_df,  Experience_df) %>%
  dplyr::mutate(text = paste(where_1, where_2, role, sep = " ")) %>%
  unnest_tokens(word, text) %>%            # split text into individual words
  filter(!word %in% stopwords("en")) %>%   # remove common stop words
  count(word, sort = TRUE)


## monochromatic palette based on https://icolorpalette.com/color/20854e (based on one of the colors from nejm palette)

word_counts_Ed_Exp %>% filter(n>1) %>%
  ggplot(aes(label = word, size = n, color =n)) +
  scale_size_area(max_size = 20)+
  geom_text_wordcloud() +
  scale_color_gradient(low = "#071F12", high = "#20854E")+
  theme_bw()+
  theme(panel.border = element_blank())


```

Projects {data-height=900}
--------------------------------------------------

### Projects timeline {data-width=600}

```{r projects timeline, echo=FALSE}
timeline_projects<- ggplot(Projects_df, aes(y = title_wrapped)) +
  geom_segment(aes(x = start_date, xend = end_date, yend = title_wrapped), color = "gray45", alpha = 0.4, linewidth = 7) +
  geom_point(aes(x = start_date, color = role_wrapped, text = title), size = 8) +
  geom_point(aes(x = end_date, color = role_wrapped, text = title), size = 6) +
  geom_text(aes(x = start_date + months(6), label = short_title), size = 3, hjust = 0)+
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  facet_grid(rows = vars(where_1_wrapped), scales = "free")+
  scale_color_simpsons(name = "Role in\n project")+
  guides(color = guide_legend(override.aes = list(size = 4)))+
  theme_minimal() +
  theme(
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_text(angle = 60, hjust = 1, size = 10),
    axis.text.y = element_blank(),
    legend.position = "bottom") +
  coord_cartesian(clip = "off")

ggplotly(timeline_projects, tooltip = "text") %>%
  layout(
    legend = list(
      orientation = "h",
      x = 0.5,
      y = -0.5,
      yref = "paper",
      xanchor = "center",
      yanchor = "top"
    ),
    margin = list(l = 70, r = 70, b = 150))

```

### Wordcloud {data-width=400}

```{r projects wordcloud, echo=FALSE}

word_counts_Projects <- Projects_df %>%
  dplyr::mutate(text = paste(where_1, where_2, title, short_title, sep = " ")) %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stopwords("en")) %>%
  count(word, sort = TRUE)


## monochromatic color palette based on https://icolorpalette.com/color/fd7446 (based on one of the colors from simpsons palette)

word_counts_Projects %>% filter(n>1) %>%
  filter(!word %in% c("university", "poznań", "wageningen")) %>% # this needs to be topic centered and university and city is not relevant
  ggplot(aes(label = word, size = n, color = n)) +
  scale_size_area(max_size = 15)+
  geom_text_wordcloud(shape = "diamond") +
  scale_color_gradient(low = "#4A1301", high = "#FD7446FF")+
  theme_bw()+
  theme(panel.border = element_blank())


```


Trainings {data-height=700}
---------------------------------------------------------------------------------------

### Trainings timeline {data-width=600}

```{r trainings timeline, echo=FALSE}
timeline_trainings<- ggplot(Trainings_df, aes(y = title_wrapped)) +
  geom_segment(aes(x = start_date, xend = end_date, yend = title_wrapped), color = "gray45", alpha = 0.6, linewidth = 4) +
  geom_point(aes(x = start_date, fill = type, text = key_outcomes), shape = 23, alpha = 0.7, size = 3) +
  geom_point(aes(x = end_date, fill = type, text = key_outcomes), shape = 23, size = 3) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  facet_wrap(~ where_1, ncol = 1, scales = "free_y")+
  scale_fill_jco(name = "Training type")+
  theme_minimal() +
  theme(
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.y = element_text(size = 10),
    axis.text.x = element_text(angle = 60, hjust = 1, size = 10),
    strip.text = element_text(face = "bold", size =12),
    legend.position = "bottom") +
  coord_cartesian(clip = "off")


ggplotly(timeline_trainings, tooltip = "text", height = 700) %>%
  layout(legend = list(
      orientation = "h",
      x = 0.5,
      y = -0.2,
      yref = "paper",
      xanchor = "center",
      yanchor = "top"),
    margin = list(l = 170, r = 70, b = 150))

```

### Wordcloud {data-width=400}

```{r trainings wordcloud, echo=FALSE}

word_counts_Trainings <- Trainings_df %>%
  dplyr::mutate(text = paste(title, type, key_outcomes, sep = " ")) %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stopwords("en")) %>%
  count(word, sort = TRUE)


## monochromatic color palette based on https://icolorpalette.com/color/0073c2 (based on one of the colors from jco palette)

word_counts_Trainings %>% filter(n>1) %>%
  ggplot(aes(label = word, size = n, color = n)) +
  scale_size_area(max_size = 15)+
  geom_text_wordcloud() +
  scale_color_gradient(low = "#001B2D", high = "#0073c2")+
  theme_bw()+
  theme(panel.border = element_blank())

```


Skills {data-height=650}
---------------------------------------------------------------------------------------

### Biostatistical skills timeline {data-width=600}

```{r biostatistical skills timeline, echo=FALSE}
timeline_biostatistical_skills<- ggplot(biostatistical_skills_df, aes(y = skill)) +
  geom_segment(aes(x = start_date, xend = end_date, yend = skill), color = "gray45", alpha = 0.4, linewidth = 8) +
  geom_point(aes(x = start_date, fill = software), shape = 21, size = 8) +
  geom_text(aes(x = start_date + months(6), label = skill), size = 3, hjust = 0, nudge_x = 500)+
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  facet_grid(rows = vars(where_1_wrapped), scales = "free")+
  scale_fill_frontiers()+
  guides(color = guide_legend(override.aes = list(size = 4)))+
  theme_minimal() +
  theme(
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_text(angle = 60, hjust = 1, size = 10),
    axis.text.y = element_blank(),
    strip.text = element_text(size =12),
    legend.position = "bottom") +
  coord_cartesian(clip = "off")

ggplotly(timeline_biostatistical_skills, height = 600) %>%
  layout(
    legend = list(
      orientation = "h",
      x = 0.5,
      y = -0.2,
      yref = "paper",
      xanchor = "center",
      yanchor = "top"
    ),
    margin = list(r = 70, b = 60))


```

### Language skills {data-width=400}

```{r language, echo=FALSE}

div(style = "margin-bottom: 100px;",
    gauge(100, min = 0, max = 100, label = "Polish, native")
)

div(style = "margin-bottom: 100px;",
    gauge(85, min = 0, max = 100, label = "English, C1")
)

div(style = "margin-bottom: 100px;",
    gauge(45, min = 0, max = 100, label = "Dutch, B1")
)

```


# Data

## Sections {.tabset}

### Education & Experience

```{r Education Experience data, echo=FALSE}
Education_Experience_df <- Education_df %>% mutate(type = "Education") %>%
  bind_rows(Experience_df %>% mutate(type = "Experience"))

datatable(Education_Experience_df)
```

### Projects

```{r Projects data, echo=FALSE}

datatable(Projects_df)

```

### Trainings

```{r Trainings data, echo=FALSE}

datatable(Trainings_df)

```

### Skills

```{r Skills data, echo=FALSE}

datatable(biostatistical_skills_df)

```